Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-25 WSSSPE3/report/wg_appendix_metrics.tex
Fix typos.

\item
Coordination (mail communication, info page etc), via WSSSPE GitHub or other?

@@

\item
Est. July 2016: By time of next CFP for WSSSPE have complete draft of white paper

\item
Est. Sept -- Oct 2016: Responses to white paper submitted to WSSSPE4

>>>>

\item
Coordination (mail communication, info page, etc.) via WSSSPE GitHub or other
means?

@@

\item
Est.\ July 2016: By the time of next CFP for WSSSPE, to have a complete draft of the white paper

\item
Est.\ Sept -- Oct 2016: Responses to white paper to be submitted to WSSSPE4

### 2016-01-25 WSSSPE3/report/wg_appendix_software_credit.tex
Fix typos.

The WSSSPE breakout group plans to join efforts related to citing software with
the FORCE11 Software Citation Working Group (FORCE11-SCWG)\footnote{FORCE11
Software Citation Working Group,
\url{https://www.force11.org/group/software-citation-working-group}}; Kyle
Niemeyer formally requested the merging of these groups following the meeting.
However, some future plans of the WSSSPE group fall outside the scope of
FORCE11-SCWG, which covers software citation practices. These activities include
working with indexers such as Web of Science and Scopus to index software
citations archived on, e.g., Zenodo or FigShare, and pursuing the development of
an open indexing service; such plans will be pursued either separately or
through the formation of follow-on FORCE11 working groups.

>>>>

The WSSSPE breakout group plans to join efforts related to citing software with
the FORCE11 Software Citation Working Group (FORCE11-SCWG)\footnote{FORCE11
Software Citation Working Group,
\url{https://www.force11.org/group/software-citation-working-group}}; Kyle
Niemeyer formally requested the merging of these groups following the meeting.
However, some future plans of the WSSSPE group fall outside the scope of
FORCE11-SCWG, which covers software citation practices. These activities include
working with indexers such as Web of Science and Scopus to index software
citations archived on, e.g., Zenodo or figshare, and pursuing the development of
an open indexing service; such plans will be pursued either separately or
through the formation of follow-on FORCE11 working groups.
